Bayesian exponential random graph modeling of KWL Burial network

### 2020-10-30 analysis/paper/paper.Rmd
adjust models and edit Intro

<!--burial study- network analysis-->
Burials contain valuable information about both individual mortuary practices and the structure of a society . The development of network science and graph theory provides many new tools for the study of the relations between burials and exploration their social implications [@Sosna2013]. Mortuary practices such as burial forms, grave goods, and related ritual practices that structure the material configuration of burials can represent social relations between members of a community, allowing the inference for social structures [citation needed]. This means we can use data from burials to study social differences to answer questions related to social inequality and complexity [@Ehrhardt2009; @Gamble2002; @Janes2013; @Johansen2015]. For example, burial goods can reflect social practices in broader cultural contexts to represent personal wealth, social roles, or traditional customs. Burials with grave goods in common often indicate some similar underlying social relations, for example, individuals that share similar access to trade, exchange, and gifting networks [@Coward2013, pp. 252]. Identifying the structure of relationships among burials can give insights into the structure of social organization.

One common way to study connections between individuals is network analysis, which has been increasingly applied by archaeologists in recent years [@Mills2017]. Networks are represented as graphs consisting of a set of actors, such as people, groups, or organizations, and a set of links connecting them [@Brughmans2018; @Robins2007]. <!-- define 'links' a bit more --> Actors are "nodes" connected by multiple "edges", representing relationships, between nodes. The basic unit of relationship is called a dyad, defined as a connection between two distinct actors [@Lee2016]. In archaeology, relationships can be viewed as flows of resources that reflect relations of control, dependence, and cooperation, indicating social relations in societies [@Marin2011]. With network analysis, we can quantify, visualize, and statistically test hypotheses about the relationships between actors to examine the structure of network and major factors that affect the formation of the structure [@Freeman2004; @Salvini2010]. Network analysis in archaeology is widely used for different topics including distribution of archaeological sites, grave goods, and social complexity [@Coward2013; @Mizoguchi2013; @Potgieter2008]

>>>>

<!--burial study- network analysis-->
Burial analysis has long developed in archaeology to study societies through mortuary practices, such as cultural and biological records in burial contexts, reflecting the social status or identity of the deceased [@Binford1971; @Saxe1970]. Despite the criticism for not considering the burial manipulation by the living or situations of less connection to real life [@Hodder1980; @Pearson1982], burial analysis with a quantitative approach is still effective to answer questions related to social representations with both archaeological contexts of death and life in mind [@Chapman2003]. Mortuary practices include burial forms, grave goods, and related ritual practices that structure the material configuration of burials can represent social relations between members of a community, allowing the inference for social structures [@Byrd1995; @Seikel2011]. The development of network science and graph theory provides many new tools for the study of the relations between burials and exploration of their social implications [@Sosna2013]. This means we can use data from burials to study social differences to answer questions related to social inequality and complexity [@Ehrhardt2009; @Gamble2002; @Janes2013; @Johansen2015]. For example, burial goods can reflect social practices in broader cultural contexts to represent personal wealth, social roles, or traditional customs. Burials with the same mortuary practices may indicate some similar underlying social relations, for example, individuals with grave goods in common that share similar access to trade, exchange, and gifting networks [eg. @Coward2013, pp. 252]. Identifying the structure of relationships among burials can give insights into the structure of social organization.

To measure relations and patterns underlying the relations, social network analysis (SNA), is a useful method that has been increasingly applied by archaeologists to study relationship between humans, or sites in past societies [@Mills2017]. A social network can be expressed as a graph consisting of a set of socially-relevant nodes, or actors, connected by edges representing one or more relations, for example, friendship, collaborations, information flow, trade ties, or any forms of connection of interest [@Marin2011; @Wasserman1994]. The basic unit of relationship is called a dyad, defined as a connection between two distinct actors [@Lee2016]. In archaeology, actors can be people, groups, objects, places, or events, with ties built on similarity, proximity, and co-presence of material culture based on archaeological theories for relationships [@Mills2017; @Brughmans2018]. This allows answering questions related to interaction and exchange, identities, and power relationships between social groups or archaeological sites by quantifying and visualizing social relations from archaeological data. There are two common approaches of archaeological applications, one is analyzing structures of networks built on archaeological data and finding patterns, and another is modeling theory to represent and test dependence of relationships [@Brughmans2018]. The modeling approach is useful to statistically test hypotheses about the relationships between actors to examine the structure of network and major factors that affect the formation of the structure [@Freeman2004; @Salvini2010]. Those approaches are widely used for different topics, such as exploring hunter-gatherer exchange network in the Kuril Islands based on ceramic compositions [@Erik2015]; long term inter-site relationship from the Epipalaeolithic to the early Neolithic in Near East according to trade items [@Coward2013]; hierarchical communication systems in the Kofun period in Japan through prestige goods [@Mizoguchi2013].
